---
title: "SOA Research"
author: "Net"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---


```{r setup, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=TRUE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

# Initial Settings
```{r message=FALSE, warning=FALSE}
# Package Loading========================
# Package Loading========================
library(tidyverse)
library(ggthemr)
library(ggthemr)
library(ggcorrplot)
ggthemr("fresh", type="outer", layout="scientific", spacing=2)
library(scales)
library(ggridges)
library(imputeTS)
# Data Loading===========================
biocpacity <- read_csv("Biocapacity by Source.csv")
co2emission <- read_csv("CO2e Emissions by SectorSource.csv")
company <- read_csv("CompanyData.csv")
ecofootprint <- read_csv("Ecological Footprint by Source.csv")

country_data <- co2emission %>%
  select(Year, population, gdp, land_area, forested_land, percent_population,
         energy_use, renewable_energy)
co2emission <- co2emission %>% 
  select(-population, -gdp, -land_area, -forested_land, -percent_population,
         -energy_use, -renewable_energy)
```
# General Assumptions

* No commission charges or extra fees during the carbon credits transaction

* 

# Data Manipulation
```{r}
# Merge in columns =======================================
biocpacity <- biocpacity %>%
  pivot_longer(c("Built_up_Land","Cropland",
                 "Fishing_Grounds","Forest_Products",
                 "Grazing_Land", "Biocapacity_Total"),
               names_to = "Type"
               )
co2emission <- co2emission %>%
  pivot_longer(c("B","E","I","O","T","W", "Emission_Total"),
               names_to = "Type")
## Hold on to the rest: ecofootprint, company
```

# Insights through Visulization
## General emission trend
```{r}
# Have a look =============================================
# DATASET: co2emission
## General emission trend
co2emission %>%
  filter(Type == "Emission_Total") %>%
  ggplot(aes(x = Year, y = value)) +
  geom_point(aes(size = log(value) * 100), alpha = 0.5) +
  geom_line(size = 1.5) +
  scale_x_continuous(breaks = c(1999, 2005, 2011, 2015, 2019)) +
  geom_vline(xintercept = 2001, linetype = 2, color = "orange", size = 1.2) +
  geom_vline(xintercept = 2011, linetype = 2, color = "orange", size = 1.2) +
  labs(x = "Year", y = "Co2e Emission") +
  ggtitle("CO2e Emission Trend",
          subtitle = "emission of co2e started dropping since 2011") +
  theme(panel.grid.major.x = element_blank(),
        legend.position = "none")
```

## Trend in different type
```{r}
## Trend in different type
co2emission %>%
  filter(Type != "Emission_Total") %>%
  ggplot() +
  geom_bar(aes(x = Year, y = value, fill = value),
           stat = "identity") +
  facet_wrap(~Type) +
  ggtitle("Emission of Sectors",
          "Max Emission Sector: Energy, Manufacturing and Construction ") +
  theme(legend.title = element_blank())
```

## Biocpacity
```{r}
# DATASET: biocpacity
## The total biocpacity didn't had many alteration
biocpacity %>%
  filter(Type != "Biocapacity_Total") %>%
  ggplot() +
  geom_bar(aes(x = Year, y = value, fill = Type), 
           stat = "identity", position = "stack") +
  labs(x = "Year", y = "Biocapacity Contribution") +
  ggtitle("Biocapacity Contribution Trend",
          "The total emission capacity and the proportion had little alteration")
```

# Tricky Companies
## About the data
See the proportion of missing values.
```{r}
all_zeros <- (company$`2019` == 0) & (company$`2018` == 0) &
       (company$`2017` == 0) & (company$`2016` == 0) &
       (company$`2015` == 0)
have_zero <- (company$`2019` == 0) | (company$`2018` == 0) |
       (company$`2017` == 0) | (company$`2016` == 0) |
       (company$`2015` == 0)
print(
  paste0("There are ", round(mean(all_zeros, na.rm = T),4)*100, 
         "% of company that have no data")
)
print(
  paste0(round(mean(have_zero, na.rm = T), 4)*100, 
         "% of company have at least one 0")
)
```

```{r}
company <- company %>%
  filter(!((company$`2019` == 0) && (company$`2018` == 0) &&
       (company$`2017` == 0) && (company$`2016` == 0) &&
       (company$`2015` == 0))) %>%
  na_if(0)
round(colMeans(is.na(company)),2)
```

Besides, there exist some companies that have multiple sectors. We just deleted those since there only a few observations. 
```{r}
table(company$`Company ID`) %>% as.data.frame() %>% arrange(-Freq) %>% head(10)
```
There are 1049 locations in total.

## Impute the missing values

* linear interpolatation

```{r warning=FALSE}
temp_df <- company %>%
  filter(!(`Company ID` %in% c(5.48531e+12, 2.45743e+13,
                               1.1289e+13, 2.02059e+13,
                               2.73896e+13, 3.66985e+13,
                               8.7252e+13, 8.82264e+13))
         ) %>%
  select(`2019`:`2015`)
rownames(temp_df) <- company %>%
  filter(!(`Company ID` %in% c(5.48531e+12, 2.45743e+13,
                               1.1289e+13, 2.02059e+13,
                               2.73896e+13, 3.66985e+13,
                               8.7252e+13, 8.82264e+13))) %>%
  pull(`Company ID`)

d <- temp_df %>%
  rownames_to_column %>%
  gather(var, value, -rowname) %>%
  spread(rowname, value)

d_noNA <- d %>% select(var) %>%
  cbind(
    na_interpolation(d[-1], option = "linear")
  )


rownames(d_noNA) <- d_noNA$var
new_company <- d_noNA %>%
  rownames_to_column %>%
  gather(var, value, -rowname) %>%
  spread(rowname, value) %>%
  mutate(var = as.numeric(var)) %>%
  rename(`Company ID` = var) %>%
  left_join(company[,c(1:3)], by = "Company ID") %>%
  select(`Company ID`, Sector, Location, everything()) %>%
  mutate_at(vars(`2015`,`2016`,`2017`,`2018`,`2019`), as.numeric) %>%
  rename(year_2015 = `2015`, year_2016 = `2016`,
         year_2017 = `2017`, year_2018 = `2018`,
         year_2019 = `2019`) %>%
  na.omit() %>%
  mutate(Company_Total = year_2015+year_2016+year_2017+year_2018+year_2019) %>%
  rename(`2015` = year_2015, `2016` = year_2016,
         `2017` = year_2017, `2018` = year_2018,
         `2019` = year_2019)  %>% 
  pivot_longer(`2015`: `2019`, 
               names_to = "Year")

```


## Insights on company data

### Sector
```{r}
new_company %>%
  group_by(`Company ID`) %>%
  ggplot() +
  geom_density(aes(log(Company_Total), fill = Sector, color = Sector), 
               alpha = 0.8) +
  labs(x = "Log(Company Total Emissions)") +
  ggtitle("Distribution of Company Total Emissions",
          "Waste and Transport are the dominant emission sources")
```

### Location
```{r}
new_company %>%
  group_by(Location) %>%
  summarise(Total_Emission = sum(Company_Total)) %>%
  ggplot() +
  geom_histogram(aes(log(Total_Emission)), fill = "darkred", alpha = 0.8) +
  labs(x = "Log(Total Emission)")
```

### Sectors & Time

```{r}
new_company %>%
  ggplot() +
  geom_boxplot(aes(x = Sector, y = log(value), fill = Year)) +
  labs(y = "Log(Company Yearly Emission)") +
  ggtitle("Sectors Weights & Yearly Trend",
          "The transport sector generate the most CO2e\nNo significant yearly trend within the sectors")
```

# Information about Pullanta
```{r}
Total_emission <- co2emission %>% filter(Type == "Emission_Total")

corr_data <- country_data %>%
  left_join(Total_emission, by = "Year") %>%
  select(-Type) %>%
  rename(Emission = value) %>%
  select(Year, Emission, everything())

corr <- round(cor(corr_data[-1] %>% scale()), 1)
p.mat <- cor_pmat(corr_data[-1] %>% scale())
ggcorrplot(corr, hc.order = T,
           type = "lower", p.mat = p.mat)
```

From the correlation graph, the CO2E emission is correlated with 

* Land Area 

* Energy Use 

* Population 

* GDP

**Specially, the emssion of greenhouse gases is highly correlated with the land area.** On the other hand, forested land, percent population, renewable energy consumption don't lay much impact on the emission of CO2e, which is quite unexpected. (*We did standardized the data by scaling and centralizing. But hence we are generating the correlation matrix, it doesn't really matter.*)
As we look over the dataset, there exist huge gaps between renewable energy use and other energy consumptions. In other words, **the renewable energy in Pullanta had slow development over these years.**

**Let's go down to the factors that mostly effect the greenhouse gases emission.**

## GDP & Popultaion
```{r fig.height=3.5, fig.width=8.5}
GrowthRate <- country_data %>% 
  # Population Rate
  mutate(
    Previous_Year = lag(population, 1), 
    Change = population - Previous_Year, 
    Population_Growth_Rate = Change/Previous_Year*100
    ) %>%
  # GDP Rate
  mutate(
    Previous_GDP = lag(gdp, 1),
    Change_GDP = gdp - Previous_GDP,
    GDP_Growth_Rate = Change_GDP/Previous_GDP*100
  ) %>%
  filter(Year != 2019, Year != 1995) %>%
  pivot_longer(c(Population_Growth_Rate, GDP_Growth_Rate), names_to = "Growth_Rates")

GrowthRate_GDP <- GrowthRate %>%
  filter(Growth_Rates == "GDP_Growth_Rate") %>%
  ggplot(aes(x = Year, y = value)) +
  geom_line(size = 1.5) +
  geom_smooth(linetype  = 2) +
  scale_x_continuous(breaks = c(1995, 2000, 2005, 2010, 2015, 2018)) +
  labs(y = "Rate(%)") +
  ggtitle("GDP growth rate")
GrowthRate_Pop <- GrowthRate %>%
  filter(Growth_Rates == "Population_Growth_Rate") %>%
  ggplot(aes(x = Year, y = value)) +
  geom_line(size = 1.5) +
  geom_smooth(linetype  = 2) +
  scale_x_continuous(breaks = c(1995, 2000, 2005, 2010, 2015, 2018)) +
  labs(y = "Rate(%)") +
  ggtitle("Population growth rate")
gridExtra::grid.arrange(GrowthRate_Pop, GrowthRate_GDP, nrow = 1)
```

## Energy Use

```{r fig.height=3.5, fig.width=8.5}
country_data %>% 
  mutate(
    Previous_Year = lag(energy_use, 1), 
    Change = energy_use - Previous_Year, 
    Energy_Growth_Rate = Change/Previous_Year*100
  ) %>%
  filter(Year != 2019, Year != 1995) %>%
  ggplot(aes(x = Year, y = Energy_Growth_Rate)) +
  geom_bar(aes(fill = Energy_Growth_Rate), stat = "identity") +
  geom_smooth(linetype = 2, alpha = 0.3) +
  theme(legend.position = "top") +
  labs(y = "Rate(%)") +
  ggtitle("Growth Rate of Energy")
```

## Land Area
```{r fig.height=3.5, fig.width=8.5}
country_data %>% 
  mutate(
    Previous_Year = lag(land_area, 1), 
    Change = land_area - Previous_Year, 
    Land_Growth_Rate = Change/Previous_Year*100
  ) %>%
  filter(Year != 2019, Year != 1995) %>%
  ggplot(aes(x = Year, y = Land_Growth_Rate)) +
  geom_bar(aes(fill = Land_Growth_Rate), stat = "identity") +
  geom_smooth(linetype = 2, alpha = 0.3) +
  theme(legend.position = "top") +
  labs(y = "Rate(%)") +
  ggtitle("Growth Rate of Land Use")
```


# Revenue and Expense
## a) Aggregate Emission
## b) Frequency and Limits
## c) Social Cost of Carbon
## d) Secondary Market
## e) Consequences
## f) Neighboring Countires

# Design Financial Instruments 
```{r}
TES <- co2emission %>%
  filter(Type != "Emission_Total") %>%
  group_by(Type) %>%
  summarise(TES = sum(value))
TES <- TES %>%
  mutate(prop = TES/sum(TES))
TES %>%
  ggplot(aes(x = "", y = prop, fill = Type)) +
  geom_bar(stat = "identity") +
  coord_polar("y") +
  labs(x = NULL, y = NULL, fill = NULL) +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        plot.title = element_text(size = 14)) +
  geom_text(aes(label = paste0(round(prop,2)*100, "%")), 
            position = position_stack(vjust = 0.5),
            check_overlap = TRUE, # 查看是否重叠
            fontface = "bold",
            size = 5) +
  ggtitle("Proportion: Each Sector")
```

## Compare & Constrast
## Risks

# Goverment perspective: Implementation
# Enterprise perspective: Risk Management


